---
title: "A3 Task 3"
author: "Samantha Kuglen"
date: "10/24/2021"
output: html_document
---
## Overview

## Data Citation

## Setup 
```{r setup, include=TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Attach packages
library(here)
library(tidyverse)
library(janitor)
library(lubridate)
library(kableExtra)

```

## Read in Data
```{r}
# Store data as new object `urchins_data` and convert col names to lower snake case
urchins_data <- read_csv(here("data", "urchins.csv")) %>% 
  clean_names()
```

## A I: Data Visualization
### Compare Distribution of Purple and Red Urchins
Compare distribution of sizes between purple and red urchins with a finalized, faceted histogram, each with 10 bins.
```{r, Fig Cap: }

ggplot(urchins_data, aes(x = size, color = common_name, fill = common_name)) +
  geom_histogram(position = "identity", 
                 alpha = 0.5,
                 bins = 10) +
  facet_wrap(~common_name) +
  labs(x = "Size (cm)", 
       y = "# of Urchins",
       title = "Size Distribution of Purple and Red Urchins",
       color = "Common Name",
       fill = "Common Name") + # prevents duplicate legend
  scale_fill_manual(values = c("purple","red")) +
  scale_color_manual(values = c("purple","red")) +
  theme(
    plot.title = element_text(hjust = 0.5)) +
  theme_minimal() 
    
  
```

## 3A II: Descriptive Statistics Table
### Create a summary table of statistics for purple and red urchins
```{r, fig.cap='Caption blah'}
# Create a finalized summary table that contains the following statistics for purple and red urchins, ignoring site as a variable

urchins_statistics <- urchins_data %>% 
  group_by(common_name) %>% 
  summarize(
    mean_size = round(mean(size, na.rm = TRUE), 1),
    median_size = round(median(size, na.rm = TRUE), 1),
    sd_size = round(sd(size, na.rm = TRUE), 1),
    sample_size = n())

urchins_statistics %>% 
  kable(col.names = c("Species",
                      "Mean (cm)",
                      "Median (cm)",
                      "Standard Deviation (cm)",
                      "Sample size (n)"),
                      digits = 1, # changes sig figs
                      caption = "Table 1 - ") %>% 
  kable_styling(full_width = FALSE,
                html_font = "Times New Roman")

  
```
3A III: Actual and % difference in mean urchin diameter

## 3B I: 
```{r}
purple_urchins <- urchins_data %>% 
  filter(common_name == "Purple Urchin") %>% 
  mutate(date = mdy(date)) %>% 
  mutate(year_new = year(date)) %>% 
  mutate(site_full = case_when(
    site == "NAPL" ~ "Naples Reef",
    site == "AQUE" ~ "Arroyo Quemado Reef",
    site == "CARP" ~ "Carpinteria Reef",
    site == "MOHK" ~ "Mohawk Reef",
    site == "IVEE" ~ "Isla Vista Reef"
  ))
```

## 3B II:
```{r}
total_purple_urchins <- purple_urchins %>% 
  group_by(site_full, year_new) %>% 
  summarize(purple_sample_size = n())

total_purple_urchins
```

```{r}
ggplot(total_purple_urchins, aes(x = year_new, y = purple_sample_size))+
  geom_line(aes(color = site_full),
            alpha = 0.6,
            size = 1) +
  scale_color_manual(values = c("blue", "orange", "red", "purple", "green")) +
  scale_x_continuous(breaks = seq(2008, 2020, 1)) +
  scale_y_continuous(breaks = seq(min(0), max(1500), by = 100)) + 
  labs(x = "Year",
       y = "Number of Purple Urchins",
       color = "Research Site",
       title = "Total Number of Purple Urchins at Each Site Per Year (KUGLEN)")
  theme_linedraw() 
  
```
The graph reflects changes in the search urchin population. Take into account -- to determine whether the changes in counts by year are reflective of actual changes in urchin population. Other possible explanations in changes for the number of purple urchins observed are

