---
title: "Task 4 - Naples Reef Purple Urchins"
author: "Samantha Kuglen"
date: "10/29/2021"
output: html_document
---
## Overview: 

## Data Citation: 

```{r setup, include=TRUE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Attach packages
library(here)
library(tidyverse)
library(janitor)
library(lubridate)
library(kableExtra)
```

## Read in the data
```{r}
# Store data as new object `urchins_data`, convert col names to lower snake case, convert date to "Date" class and add a new column for year to use as a variable for filtering
urchins_data <- read_csv(here("data", "urchins.csv")) %>% 
  clean_names() %>% 
  mutate(date = mdy(date)) %>% 
  mutate(year = year(date))
```

## Data Wrangling
```{r}
# Compare mean size of Naples 2010 purple urchins in CONTROL and ANNUAL treatments
naples_purple_urchins <- urchins_data %>% 
  filter(year %in% c("2010"), 
         common_name %in% c("Purple Urchin"), 
         site %in% "NAPL") 

naples_stats_2010 <- naples_purple_urchins %>% 
  group_by(treatment) %>% 
  summarize(mean_size = round(mean(size, na.rm = TRUE), 1),
            median_size = round(median(size, na.rm = TRUE), 1),
            sd_size = round(sd(size, na.rm = TRUE), 1),
            sample_size = n()) 

```

## Data Visualization: Exploratory
Exploratory Faceted Histograms and QQ-plots for the size distribution of purple urchins at Naples in 2010, separated by treatment (Control and Annual) to assess normality. 

```{r}
# Histogram
ggplot(naples_purple_urchins, aes(x = size, fill = treatment, color = treatment)) +
  geom_histogram(bins = 10, 
                 alpha = 0.5) +
  facet_wrap(~ treatment) +
  labs(x = "Size (cm)",
       y = "Number of Urchins",
       title = "Size Distribution of Naples Urchins By Treatment in 2010 (KUGLEN)",
       subtitle = "Annual (Kelp Removal) vs Control (No Kelp Removal)",
       color = "Treatment",
       fill = "Treatment") + 
  theme(plot.title = element_text(hjust = 0.5,
                                  vjust = 0.2),
        plot.subtitle = element_text(hjust = 0.5,
                                     vjust = 0.2)) 

# QQ Plot
ggplot(naples_purple_urchins, aes(sample = size)) + 
  geom_qq()+
  facet_wrap(~treatment)
         
```

The distribution of purple urchin sizes

## Data Visualization II: Finalized
Summary table of descriptive statistics for both groups. 
```{r}
naples_stats_2010 %>% 
  kable(col.names = c("Treatment Type",
                      "Mean (cm)",
                      "Median (cm)",
                      "Standard Deviation (cm)",
                      "Sample Size (n)"),
        caption = "Table 1: Comparison of Naples Reef Purple Urchin Sizes (cm) from Annual and Control Treatments in 2010") %>% 
  kable_styling(full_width = FALSE,
                html_font = "Times New Roman")
```

